How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-06-13 Draft_June_2022/Full_draft_20220608.rmd
added regression plot

Additionally, @bacchi2009 [p. 10] argues that policies have a cultural dimension as "it takes shape within specific historical and national or international contexts". The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed. The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.\@hirschman1975[p. 388] exemplifies chosen problems with the case of the construction of Brasilia. Building Brasilia could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three. It is up to the discretion of the government to highlight or not the implicit problem a policy solves. A same policy object (e.g. Brasilia, the Amazon, criminality, poverty), thus, can be constructed as pressing or not depending on how a government represents it.

@@

```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation", "Social Economic",
                                            "Sovereign Conservation", 
                                            "Economic, Social,\nand Conservation",
                                            "Economic Sovereignty", "Social Conservation", "Other")),
         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
                                     location, ignore.case = TRUE), # minor coding issues to fix
                               "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat), # minor coding issues to fix
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries", location_cat),
                               levels = c("International", "Amazonian States",
                                          "Amazonian Countries", "Brasilia", "Non Amazonian States")))
# plot
mplot <- ama_model %>%
  select(con_vs_all, km_to_manaus) %>%
  ggplot(aes(x = km_to_manaus, y = con_vs_all)) +
  geom_smooth(se = FALSE, size = .5, color = "darkgreen") +
  scale_y_continuous(labels = percent_format()) +
  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), linetype = "dotted") +
  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), y = 0.5,
                    label = c("Brasilia", "New York", "Paris", "Cape Town", "Beijing"), alpha = 0.4) +
  labs(x = "Distance to Manaus (km)",
       y = "Environmental conservation",
       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
mplot
mplot_all <- ama_model %>%
  select(con_vs_all, EI_vs_all, SD_vs_all, sov_vs_all, km_to_manaus) %>%
  rename("Pure Conservation" = con_vs_all,
         "Pure Economic Integration" = EI_vs_all,
         "Pure Social Development" = SD_vs_all, 
         "Pure Sovereignty" = sov_vs_all) %>% 
  pivot_longer(-km_to_manaus, names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = km_to_manaus, y = value, color = variable)) +
  geom_smooth(se = FALSE, size = .5) +
  scale_y_continuous(labels = percent_format()) +
  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), linetype = "dotted") +
  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), y = 0.5,
                    label = c("Brasilia", "New York", "Paris", "Cape Town", "Beijing"), alpha = 0.4) +
  labs(x = "Distance to Manaus (km)",
       y = "Problem Construction",
       title = "Amazon problem constructions in relation to distance to Manaus",
       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
          legend.position = "bottom")
mplot_all
# model
model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
             family = binomial(link = 'logit'), data = ama_model)
# summary statistics
summary(model)

>>>>

Additionally, @bacchi2009 [p. 10] argues that policies have a cultural dimension as "it takes shape within specific historical and national or international contexts". The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed. The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems. @hirschman1975 [p. 388] exemplifies chosen problems with the case of the construction of Brasilia. Building Brasilia could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three. It is up to the discretion of the government to highlight or not the implicit problem a policy solves. A same policy object (e.g. Brasilia, the Amazon, criminality, poverty), thus, can be constructed as pressing or not depending on how a government represents it.

@@

```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation", "Social Economic",
                                            "Sovereign Conservation", 
                                            "Economic, Social,\nand Conservation",
                                            "Economic Sovereignty", "Social Conservation", "Other")),
         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
                                     location, ignore.case = TRUE), # minor coding issues to fix
                               "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat), # minor coding issues to fix
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries", location_cat),
                               levels = c("International", "Amazonian States",
                                          "Amazonian Countries", "Brasilia", "Non Amazonian States")))
# model
model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
             family = binomial(link = 'logit'), data = ama_model)
# summary statistics
stargazer::stargazer(model, type = "text")
# Plot model
ama_model$predicted = predict(model, ama_model, type = "response")
ggplot(ama_model, aes(x = km_to_manaus, y = predicted)) + 
  geom_smooth(size = .5, color = "darkgreen") +
    labs(x = "Distance to Manaus (km)",
       y = "Environmental conservation",
       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
       caption = "Curve in the plot is smoothed using loess method.") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
